---
title: "Lab 1 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# OU MATH-4793/5793
The R code used to load the package is the following:
```{r setup}
library(Lab1Intro)
```

## Package Functions Descriptions

### SampleMeanVector
This function takes in a dataframe or matrix, and returns a vector of the means from the columns. Calling the function would look like the following:

### SampleBiasedCovarianceMatrix
Given a matrix of data, an algorithm is employed to calculate the sample covariance and variance (biased) matrix. The variance values are located on the diagonal of the matrix, $x_{11}$,$x_{22}$...$x_{pp}$; while the covariance values are located in the other positions. Note: Uses SampleMeanVector function.

### SampleCorrelationMatrix
Given a matrix of data, an algorithm is employed to calculate the sample correlation coefficient matrix. Note: Uses SampleBiasedCovarianceVarianceMatrix function.

# Lab 1 Work

## Web Link
Web Link to GitHub Public Repository Address:
<https://github.com/OUStudent/Lab1Intro>

## Latex
Sample Mean (1-1):

$$
\bar x_k = \frac{1}{n} \sum_{j=1}^n x_{jk} \ \ k =1,2,...,p
$$

Sample Covariance (1-4):

$$
s_{jk} = \frac{1}{n} \sum_{j=1}^n (x_{ji}-\bar x_i)(x_{jk}-\bar x_k)
$$

Pearson's Product Moment Correlation Coefficient (1-5):

$$
r_{ik}=\frac{S_{ik}}{\sqrt{S_{ii}}\sqrt{S_{kk}}}=\frac{\sum_{j=1}^n (x_{ji}-\bar x_i)(x_{jk}-\bar x_k)}{\sqrt{\sum_{j=1}^n(x_{ji}-\bar x_i)^2}\sqrt{\sum_{j=1}^n(x_{jk}-\bar x_k)^2}}
$$

Figure (3-27):

$$
S=\frac{1}{n-1} X^{'}(I-\frac{1}{n}11^{'})X 
$$

Figure (3-28):

$$
D^{1/2}_{(p\ x \ p)}=
\begin{bmatrix}
  \sqrt{S_{11}} & 0 & \dots & 0 \\ 
  \vdots & \sqrt{S_{22}} & \dots & 0\\ 
  \vdots & \vdots & \ddots & \vdots \\
  0 & 0 & \dots & 0.77\\ 
\end{bmatrix}
$$

Figure (3-29):

$$
R = D^{-1/2}SD^{-1/2}
$$

## Using Package Functions for data given in Table 1.2
Loading the file and creating the data frame.
```{r}
x=read.table("Lab1.DAT",header=FALSE)
```

### Sample Mean
```{r}
Lab1Intro::SampleMeanVector(x)
```

### Sample Covariance (Biased)
```{r}
Lab1Intro::SampleBiasedCovarianceVariance(x)
```

### Sample Correlation
```{r}
Lab1Intro::SampleCorrelationMatrix(x)
```

## Assesments
### Clicker Quizes       10%
### Assignments          20%
### Laboratories         10%
### Mid Semester Exam 1  10%
### Mid Semester Exam 2  10%
### Final Exam           30%
### Projects             10%

